Repairing cooperation through a cognitive intervention in the repeated Trust Game

### 2023-08-14 article.Rmd

  trans_prob <- data.frame(
    from = rep(1:ns, each=100*ns),
    to = rep(1:ns, each=100),
    investment = seq(0,20,length=100),
    prob_pre = 0,
    prob_ctrl = 0,
    prob_coax =0
  )

@@

@@

coax_pre_plot <- ggplot(trans_prob,aes(x=investment,y=prob_coax, colour = as.factor(to))) + 
  geom_line() + 
  geom_line(aes(y=prob_pre),linetype="dotted") +
  facet_wrap(~from) + 
  ylim(c(0,1)) + 
  ggtitle("Transition function pre- and post-intervention manipulation") + 
  labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + 
  theme_bw()

>>>>

  trans_prob <- data.frame(
    from = rep(1:ns, each=100*ns),
    to = rep(1:ns, each=100),
    investment = seq(0,8,length=100),
    prob_pre = 0,
    prob_ctrl = 0,
    prob_coax =0
  )

@@

plot_state_transitions(tr_fdmod_5,numCovIn=2, numCovTr=6)

@@

# coax_pre_plot <- ggplot(trans_prob,aes(x=investment,y=prob_coax, colour = as.factor(to))) + 
#   geom_line() + 
#   geom_line(aes(y=prob_pre),linetype="dotted") +
#   facet_wrap(~from) + 
#   ylim(c(0,1)) + 
#   ggtitle("Transition function pre- and post-intervention manipulation") + 
#   labs(x = "Investment", y = "Transition probability", color='State Transitioned to') + 
#   theme_bw()

coax_pre_plot <- ggplot(trans_prob,aes(x=investment)) + 
  geom_line(aes(y=prob_coax, colour = as.factor(to), linetype="Post-intervention")) + 
  geom_line(aes(y=prob_pre, colour = as.factor(to), linetype="Pre-intervention")) +
  facet_wrap(~from) + 
  ylim(c(0,1)) + 
  ggtitle("Transition function pre- and post-intervention manipulation") + 
  labs(x = "Investment", y = "Transition probability", color='State Transitioned to', linetype = "Line Type") + 
  scale_linetype_manual(values = c("Post-intervention" = "solid", "Pre-intervention" = "dotted")) +
  theme_bw()
